Measuring Bibliometric Coverage of German Law Journals

### 2025-04-22 docs/paper.qmd
Fix date

---
title: Measuring Bibliometric Coverage of German Law Journals
author:
- name: Christian Boulanger
  orcid: 0000-0001-6928-3246
  email: boulanger@lhlt.mpg.de
  affiliation:
  - name: Max Planck Institute for Legal History and Legal Theory
    city: Frankfurt
    country: Germany
    url: https://www.lhlt.mpg.de/
- name: Daniel Fejzo
  email: fejzo@lhlt.mpg.de
  affiliation:
    - name: Max Planck Institute for Legal History and Legal Theory
      city: Frankfurt
      country: Germany
      url: https://www.lhlt.mpg.de/
- name: Christine Rimmert
  orcid: 0009-0001-2972-2061
  email: Christine.Rimmert@fiz-Karlsruhe.de
  affiliation:
    - name: FIZ Karlsruhe – Leibniz-Institut für Informationsinfrastruktur
      city: Karlsruhe 
      country: Germany
      url: https://www.fiz-karlsruhe.de
abstract: "Bibliometric analyses are uncommon in German legal scholarship, often attributed to disciplinary skepticism. However, this paper posits that a more fundamental reason is the lack of adequate data coverage in standard bibliometric databases. We systematically investigate the representation of the German law journal landscape in Web of Science (WoS), Scopus, and OpenAlex. To achieve this, we first establish a gold standard list of 52 representative German law journals based on a 2009 expert survey. We then measure the coverage of these journals within the target databases and assess the quality of the available metadata, focusing particularly on OpenAlex due to its superior initial coverage. Our findings confirm the initial hypothesis: coverage in WoS and Scopus is minimal. While OpenAlex includes a larger proportion of the gold standard journals (32/52) and shows reasonable item-level completeness for a subset checked against publisher data, its metadata quality presents significant limitations. Crucially, affiliation data is sparse, and citation data is almost entirely absent, precluding meaningful citation analysis, impact assessment, or reliable institutional evaluation. We conclude that while coverage is improving, particularly through open platforms like OpenAlex, the current state of bibliometric data, especially the lack of citation information, severely restricts the application of standard bibliometric methods to German legal scholarship. We discuss potential reasons for this gap and suggest focusing on enhancing open data repositories and exploring new methods to generate currently unavailable citation data."
lang: en
date: 2025-02-19
licence: "CC BY"
code-fold: true
project:
  execute-dir: project
execute: 
  cache: true
  echo: false
zotero: true
funding: "The authors received no specific fundings for this work."
bibliography: references.bib
csl: ieee-with-url.csl
format:
  docx: 
    toc: false
    code-annotations: none
  pdf: 
    toc: true
    code-annotations: none
  html:
    toc: true
    embed-resources: false
---

>>>>

---
title: Measuring Bibliometric Coverage of German Law Journals
author:
- name: Christian Boulanger
  orcid: 0000-0001-6928-3246
  email: boulanger@lhlt.mpg.de
  affiliation:
  - name: Max Planck Institute for Legal History and Legal Theory
    city: Frankfurt
    country: Germany
    url: https://www.lhlt.mpg.de/
- name: Daniel Fejzo
  email: fejzo@lhlt.mpg.de
  affiliation:
    - name: Max Planck Institute for Legal History and Legal Theory
      city: Frankfurt
      country: Germany
      url: https://www.lhlt.mpg.de/
- name: Christine Rimmert
  orcid: 0009-0001-2972-2061
  email: Christine.Rimmert@fiz-Karlsruhe.de
  affiliation:
    - name: FIZ Karlsruhe – Leibniz-Institut für Informationsinfrastruktur
      city: Karlsruhe 
      country: Germany
      url: https://www.fiz-karlsruhe.de
abstract: "Bibliometric analyses are uncommon in German legal scholarship, often attributed to disciplinary skepticism. However, this paper posits that a more fundamental reason is the lack of adequate data coverage in standard bibliometric databases. We systematically investigate the representation of the German law journal landscape in Web of Science (WoS), Scopus, and OpenAlex. To achieve this, we first establish a gold standard list of 52 representative German law journals based on a 2009 expert survey. We then measure the coverage of these journals within the target databases and assess the quality of the available metadata, focusing particularly on OpenAlex due to its superior initial coverage. Our findings confirm the initial hypothesis: coverage in WoS and Scopus is minimal. While OpenAlex includes a larger proportion of the gold standard journals (32/52) and shows reasonable item-level completeness for a subset checked against publisher data, its metadata quality presents significant limitations. Crucially, affiliation data is sparse, and citation data is almost entirely absent, precluding meaningful citation analysis, impact assessment, or reliable institutional evaluation. We conclude that while coverage is improving, particularly through open platforms like OpenAlex, the current state of bibliometric data, especially the lack of citation information, severely restricts the application of standard bibliometric methods to German legal scholarship. We discuss potential reasons for this gap and suggest focusing on enhancing open data repositories and exploring new methods to generate currently unavailable citation data."
lang: en
date: 2025-04-22
licence: "CC BY"
code-fold: true
project:
  execute-dir: project
execute: 
  cache: true
  echo: false
zotero: true
funding: "The authors received no specific fundings for this work."
bibliography: references.bib
csl: ieee-with-url.csl
format:
  docx: 
    toc: false
    code-annotations: none
  pdf: 
    toc: true
    code-annotations: none
  html:
    toc: true
    embed-resources: false
---
